Students' Alcohol Consumption impacts on academic Results on the example of a secondary Scool Maths Class in Portugal

### 2016-10-13 MSproject.Rmd
comission -> commission

Recent events in the world economy have lead to the decline in economic performance in many countries, amongst which is the decline of econommic growth in the European Union (EU).  As a response to these changes,  the EU has made it a priority to reverse this trend through investments that would provide new jobs and create a better educated workforce. Hence, the European Comission (EC) has set up a ‘Strategy for smart, sustainable and inclusive growth’ (European Comission, 2010), where a crucial part of investment is to contribute to the education of the next generations: The aim is to reduce the share of early school leavers to below 10% and ensure that at least 40% of the younger generation obtain a tertiary degree.

>>>>

Recent events in the world economy have lead to the decline in economic performance in many countries, amongst which is the decline of econommic growth in the European Union (EU).  As a response to these changes,  the EU has made it a priority to reverse this trend through investments that would provide new jobs and create a better educated workforce. Hence, the European Commission (EC) has set up a ‘Strategy for smart, sustainable and inclusive growth’ (European Comission, 2010), where a crucial part of investment is to contribute to the education of the next generations: The aim is to reduce the share of early school leavers to below 10% and ensure that at least 40% of the younger generation obtain a tertiary degree.
